---
title: "Project Initiation Instructions"
author: "Bobby Dominy"
date: "2023-04-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initiating a New Project

1. Create a new repo on Github
2. Clone github repo in rStudio using
```{r, eval=FALSE}
usethis::create_from_github("url-copied-from-github", 
                            destdir = "file-path-to-directory-that-will-house-repo/")
```
3. Generate filing system structure via `cabinets`, using `here()` to reference the parent directory.
```{r, eval=FALSE}
usethis::create_from_github("url-copied-from-github", 
                            destdir = "file-path-to-directory-that-will-house-repo/")
```
4. Create project-specific library source using `groundhog`.
```{r, eval=FALSE}
usethis::create_from_github("url-copied-from-github", 
                            destdir = "file-path-to-directory-that-will-house-repo/")
```
5. Create project-specific functions file.
6. Implement Analysis
7. Resolve conflicts in project-specific functions file, push to github. 

